---
title: "Homework 8"
author: "Allyson Wood"
date: "10/14/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(matrixStats)

# Read in the data and filter for these two varieties
bioData1 <- readr::read_csv("/Users/babyrenegade/Google Drive/NCSU/Fall 2019/ST558/HW/HW8/concentration.csv")
bioData <- bioData1 %>% filter(variety == "M.giganteus" | variety == "S.ravennae")
```

# Q1 
Use a for loop to implement the bootstrap for fitting a quadratic model using concentration as the predictor and Total_lignin as the response. Report an estimate of the maximum with a corresponding standard error.
```{r forloop, echo=TRUE}
n <- dim(bioData)[1] ## number of obs in data
B <- 10000 ## number of bootstrap samples
results <- matrix(data = NA, nrow = B, ncol = 1, dimnames = list(NULL, c("concentration")))
for(b in 1:B) {
  i = sample(x = 1:n, size = n, replace = TRUE) ## sample indices
  temp = bioData[i,] ## temp data set
  fit <- lm(Total_lignin~concentration+I(concentration^2), data=temp) #fit model
  results[b,] <- - fit$coefficients[2] / (2*fit$coefficients[3]) #calculate max estimate
}
results[1,] #output a max estimate
colSds(results) #calc SE of the distribution of max estimates generated w/ for loop
```

# Q2  
Redo the bootstrap analysis for the Total_lignin response using the replicate function.
``````{r function, echo=TRUE}
# Function takes in dataset name, predictor var, and response to produce one resample
bootFun <- function(data,resp,pred) {
  sub <- as.data.frame(select(data, resp, pred))
  b <- sample_n(sub, size=dim(sub)[1], replace=TRUE)
  fit = lm(b[,1]~b[,2]+I(b[,2]^2))
  beta1 <- fit[[1]][2]
  beta2 <- fit[[1]][3]
  maxEst = - beta1 / (2*beta2)
  return(unname(maxEst))
}
# Resample the data 10k times & output a max estimate and the standard error
se <- replicate(10000,bootFun(bioData,"Total_lignin","concentration"))
se[1]
colSds(as.matrix(se))
```


# Q3 
Create a wrapper function for replicate that will return the standard deviation of the bootstrapped
estimates.
``````{r wrapper, echo=TRUE}
# Function takes in dataset name, response var, predictor var, and number of resample
# replications desired
seBootFun <- function(B, data, resp, pred) {
  d <- replicate(B,bootFun(data,resp,pred))
  d[1]
  colSds(as.matrix(d))
  return(list(d[1],colSds(as.matrix(d))))
}
# Max estimate and standard error of Glucose
seBootFun(B=10000, data=bioData, resp="Glucose",pred="concentration")
```

# Q4 
Use parallel computing to send each of the four bootstrap standard error computations (one for each
response) to a different core. Report estimates of each maximum (no need to find these with parallel computing) with corresponding standard errors.
``````{r parallel, echo=TRUE}
# Find the Max Estimtes and SE's before we start parallel stuff
lignin <- seBootFun(B=10000, data=bioData, resp="Total_lignin",pred="concentration")
glucose <- seBootFun(B=10000, data=bioData, resp="Glucose",pred="concentration")
xylose <- seBootFun(B=10000, data=bioData, resp="Xylose",pred="concentration")
arabinose <- seBootFun(B=10000, data=bioData, resp="Arabinose",pred="concentration")
names(lignin)  <- c("Max","SE")
names(glucose) <- c("Max","SE")
names(xylose) <- c("Max","SE")
names(arabinose) <- c("Max","SE")
lignin
glucose
xylose
arabinose

library(parallel)
# Find the number of cores on machine
cores <- detectCores()  
cores
# Define the size of the cluster for parallel processing
cluster <- makeCluster(cores-1)  
cluster

# Export functions and libraries needed for parallel processing
clusterExport(cluster, list("bootFun","seBootFun"))
clusterEvalQ(cluster, library(tidyverse))
clusterEvalQ(cluster, library(matrixStats))

# Send the seBootFun() function to different cores for each response variable
parResults <- parLapply(cl = cluster,
                        X= c("Total_lignin","Glucose","Xylose","Arabinose"),
                        fun = seBootFun,
                        data=bioData,
                        B=10000,
                        pred="concentration")

names(parResults) <- c("Lignin","Glucose","Xylose","Arabinose")
finalResults <- unlist(parResults)
names(finalResults) <- c("Lignin Max","Lignin SE",
                         "Glucose Max","Glucose SE",
                         "Xylose Max","Xylose SE",
                         "Arabinose Max","Arabinose SE"
                         )
finalResults
```